\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-06 paper/ms.tex
putting the code in the paper
threshold_fraction argument

\begin{align}
\mu &\sim \textnormal{Uniform}(-10, 10)\\
\ln\sigma &= \textnormal{Uniform}(-10, 10)\\
n_i &= \textnormal{Normal}(0, 1)
\end{align}
where each of the $n_i$ enables a data point to be calculated using
\begin{align}
x_i &= \mu + \sigma n_i.
\end{align}
A general procedure for achieving this is to imagine generating a
simulated data set from the parameters. In this process, you would need
to call a random number generator many times.
The results of the random number calls
are independent of the parameters and
can be used to parameterize the data set. In the example,
the $\{n_i\}$ variables play this role.

@@

For ABC applications, there is an alternate \code{postprocess()} function:
\begin{CodeChunk}
\begin{CodeInput}
import dnest4.classic as dn4
dn4.postprocess_abc()
\end{CodeInput}
\end{CodeChunk}

>>>>

\begin{align}
\mu &\sim \textnormal{Uniform}(-10, 10)\\
\ln\sigma &= \textnormal{Uniform}(-10, 10)\\
n_i &= \textnormal{Normal}(0, 1)
\end{align}
where each of the $n_i$ enables a data point to be calculated using
\begin{align}
x_i &= \mu + \sigma n_i.
\end{align}
A general procedure for achieving this is to imagine generating a
simulated data set from the parameters. In this process, you would need
to call a random number generator many times.
The results of the random number calls
are independent of the parameters and
can be used to parameterize the data set. In the example,
the $\{n_i\}$ variables play this role.
Therefore, the variables in the model class are:
\begin{CodeChunk}
\begin{CodeInput}
class MyModel
{
    private:
        double mu, log_sigma;
        std::vector<double> n;
\end{CodeInput}
\end{CodeChunk}

@@

For ABC applications, there is an alternate \code{postprocess} function
called \code{postprocess_abc}.
This generates posterior samples using the $\epsilon$ value that
compresses the joint prior by 80\% as much as the final level.
\begin{CodeChunk}
\begin{CodeInput}
dnest4.classic.postprocess_abc()
\end{CodeInput}
\end{CodeChunk}
To try different values of $\epsilon$, you can set the argument
\code{threshold\_fraction} to a value other than 0.8. For example
\begin{CodeChunk}
\begin{CodeInput}
dnest4.classic.postprocess_abc(threshold_fraction=0.6)
\end{CodeInput}
\end{CodeChunk}
